Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-12 doc/slides/hong+eisner.TLT13.slides.tex
slides so far.
slides so far. Added a new intro slide with visualization. Still discussing with Jason what to do with the reversed subject arc.

@@

\begin{itemize}
\item This is due to an inconsistency of the Link Grammar, discovered by our method. 
\end{itemize}

@@

\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  Jill \& persuaded \& him \& to \& skip \\
	\end{deptext}
    \deproot[edge above, edge unit distance=2ex]{1}{W}
    \deproot[edge above, edge unit distance=2ex]{2}{WV}
	\depedge[edge above]{2}{1}{S}
	\depedge[edge above]{2}{3}{O}
	\depedge[edge above]{2}{4}{TO}
	\depedge[edge above]{4}{5}{I}
	\depedge[edge above]{2}{5}{IV}
  \end{dependency}
\end{figure}

>>>>

\frame{\frametitle{Single-headedness}
  Dependency parse treebanks today are single-headed.

\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	\end{deptext}
	\deproot[edge above, thick, edge style = {blue}]{3}{\small ROOT}
	\depedge[edge above, thick, edge style = {blue}]{3}{2}{\small SBJ}
	\depedge[edge above, thick, edge style = {blue}]{3}{4}{\small ADV}
	\depedge[edge above, thick, edge style = {blue}]{3}{5}{\small ADV}
	\depedge[edge above, thick, edge style = {blue}]{3}{6}{\small VC}
	\depedge[edge above, thick, edge style = {blue}, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge above, thick, edge style = {blue}]{2}{1}{\small NMOD}
	\depedge[edge above, thick, edge style = {blue}]{7}{8}{\small ADV}
	\depedge[edge above, thick, edge style = {blue}]{6}{7}{\small VC}
	\depedge[edge above, thick, edge style = {blue}]{8}{9}{\small PMOD}
  \end{dependency}
  \caption*{Some example dependency parse.}
\end{figure}

@@

\begin{itemize}
\item In our paper we claimed this was due to an inconsistency of the Link Grammar, discovered by our method.

@@

%\begin{figure}
%  \begin{dependency}
%	\begin{deptext}
%	  Jill \& persuaded \& him \& to \& skip \\
%	\end{deptext}
%    \deproot[edge above, edge unit distance=2ex]{1}{W}
%    \deproot[edge above, edge unit distance=2ex]{2}{WV}
%	\depedge[edge above]{2}{1}{S}
%	\depedge[edge above]{2}{3}{O}
%	\depedge[edge above]{2}{4}{TO}
%	\depedge[edge above]{4}{5}{I}
%	\depedge[edge above]{2}{5}{IV}
%  \end{dependency}
%\end{figure}

\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  Jill \& thinks \& he \& will \& skip \\
	\end{deptext}
    \deproot[edge above, edge unit distance=2ex]{1}{W}
    \deproot[edge above, edge unit distance=2ex]{2}{WV}
	\depedge[edge above]{1}{2}{S}
	\depedge[edge above]{2}{3}{C}
	\depedge[edge above]{3}{4}{S}
	\depedge[edge above]{4}{5}{I}
	\depedge[edge above]{2}{5}{CV}
  \end{dependency}
\end{figure}
